A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Introduction again

Figure~\ref{subfig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead, dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{subfig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{subfig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (\overline{B} \land C)$.}
    \label{fig:bdd-and-obdd}
\end{figure}

@@

Already in 1986, Bryant~\cite{BRYANT86} noticed that some classes of Boolean
functions cannot be represented by an OBDD efficiently, regardless of the variable
ordering chosen. He then studied the complexity of Boolean functions in
1991~\cite{BRYANT91} to provide a lower bound on the OBDD as data structure (and
very large scale integrated circuits). The complexity was expressed in the minimum
size of the OBDD, i.e. the minimal number of nodes for any possible variable
ordering $\pi$. Bryant~\cite{BRYANT91} mainly focused on the set of integer
multipliers having word size $n$.

>>>>

Figure~\ref{subfig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (\neg B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead, dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{subfig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{subfig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (\neg B \land C)$.}
    \label{fig:bdd-and-obdd}
\end{figure}

@@

Already in 1986, Bryant~\cite{BRYANT86} noticed that some classes of Boolean
functions cannot be represented by an OBDD efficiently, regardless of the variable
ordering chosen. He then studied the complexity of Boolean functions in
1991~\cite{BRYANT91} to provide a lower bound on the OBDD as data structure (and
very large scale integrated circuits). The complexity was expressed in the minimum
size of the OBDD, i.e. the minimal number of nodes for any possible variable
ordering $\pi$. Bryant~\cite{BRYANT91} mainly focused on the set of integer
multipliers (having word size $n$).
